\Large \bf Dark Decoys: Conjuring Proxies from Unused Address Space

### 2019-02-15 paper/paper.tex
edit arch section to emphasize ipv6

Dark Decoys involve three main steps. First, clients \textbf{register} with the
ISP station,
and agree on the dark decoy IP address that will be used. Next, the client
connects to the agreed upon address, which is terminated by an
\textbf{application} running on the station. Finally, the client \textbf{proves}
to the application that it was the same entity that registered (and not a censor
attempting to probe), and is able to use the application as a proxy.

@@

To register, clients connect to a \textbf{decoy} site that supports TLS. They
complete the handshake, and send a normal HTTPS request. In TLS, requests (and
responses) are encrypted and sent in an \texttt{Application Data} record. During
registration, the client alters the ciphertext of the \texttt{Application Data} record to
convey a short \textbf{tag} to the ISP station, on path between the client and
decoy site.

The tag contains a public key (encoded to be indistinguishable from random using
Elligator~\cite{elligator}), and a message encrypted under the shared secret
derived from a key exchange with the station's long-term public key hard-coded
in the client software. The station uses its private key to compute the same
shared secret from the (decoded) public key, and decrypts the message in the
tag. The censor, without knowledge of either the station or client's private
key, cannot derive the shared secret, preventing it from being able to decrypt
the message, or learn of its existence.

Inside the message, the client communicates a random \textbf{seed}, and other
configuration-specific information, such as flags to signify version, feature
support, and which set of dark decoy network prefixes the client knows of. The
client and server use a hash of the provided seed to determine which specific
dark decoy IP address to register. It may seem intuitive to instead have the client
send the specific IP address to register, but allowing the client arbitrary
choice also allows the censor to register suspected dark decoys and block them if
they pick up. By using a hash, the censor would have to pre-image the hash to
obtain a seed it could use to register for a desired IP address. \nikita{Are we claiming that this kind of enumeration is hard to do in IPv4?} It also gives a
secret (the seed) that only the client and station know, even after the client
connects to the dark decoy address.

Once the dark decoy IP address has been selected, the station watches for
packets destined to that address, and forwards them onto the dark decoy
\textbf{application}. The station can also optionally ignore packets not from
the source IP address of the registering client, so that to a probing censor,
the dark decoy appears to be firewalled off from all but the client.

%-IPv6 vs IPv4 dark decoys subsection?

\subsection{Address utilization}
% TODO:Can be better: story for v4, these are some problems, here's what it
% looks like in v6

% Note on IPv6 space? /32 of IPv6 is 96-bits to select...
Dark decoy IP addresses are selected from unused but still routed address
space that passes by the ISP. Traffic to unrouted addresses would produce ICMP
responses that a censor could observe, and are also easily blocked with knowledge
of a routing table. Because we support the use of IPv6 addresses, censors will
also be unable to scan ahead of time to determine if the host has been there
previously, or what was there before. While they can probe suspected dark decoy
addresses after clients connect to them, at that point the address has already been
registered, preventing the censor from identifying differences in behavior
before and after registration.

While address utilization in IPv4 is quite high (all blocks have been allocated
at the RIR level), the fraction of addresses that respond to TCP connections on
a given port is quite low: even popular ports like 443 (use by TLS) have less
than 2\% of IPv4 hosts respond to connection requests. This leaves a large
number of hosts available to use as dark decoys. However, if a client registers
a dark decoy address that is already happens to be used by an existing host,
there will be multiple responses when the client tries to connect, and the
connection will fail. However, this failure is still limited to the registering
client, as the application only responds to the IP of the client that
registered. In IPv6, the odds of picking a legitimate host are negligible: with
a /32 prefix of IPv6, there are $2^{96}$ addresses to choose from.
\nikita{/32 is pretty big, e.g. UIUC only has a /48}

>>>>

Dark Decoys involve three main steps. First, clients \textbf{register} with the
ISP station,
and agree on the dark decoy IP address that will be used. Next, the client
connects to the agreed upon address, which is terminated by an
\textbf{application} running on the station. Finally, the client \textbf{proves}
to the application that it was the same client that registered (and not a censor
attempting to probe), and is able to use the application as a proxy.

@@

To register, clients connect to a \textbf{decoy} site that supports TLS. They
complete the handshake, and send a normal HTTPS request that embeds a special
steganographic \textbf{tag} in the ciphertext of the request. We use
the same technique used in TapDance's covert ciphertext channel\footnote{Section 3 in
TapDance~\cite{tapdance14}} to embed the tag, but we purposefully have the client
send a complete request (rather than incomplete), allowing the decoy server to respond.
The steganographic tag is only visible to the ISP station, which can see the tag using its
private key. Unlike in TapDance, the \scheme station can passively observe
the tag, and does not need to respond to it (which requires mimicking the
decoy)

The tag contains a public key (encoded to be indistinguishable from random using
Elligator~\cite{elligator}), and a message encrypted under the shared secret
derived from a key exchange with the station's long-term public key hard-coded
in the client software. The station uses its private key to compute the same
shared secret from the (decoded) public key, and decrypts the message in the
tag. The censor, without knowledge of either the station or client's private
key, cannot derive the shared secret, preventing it from being able to decrypt
the message, or even learn of its existence.

Inside the message, the client communicates a random \textbf{seed}, and other
configuration-specific information, such as flags to signify version, feature
support, and a set of IPv6 network prefixes that the client knows can be used
for dark decoys (previously distributed publicly).
The client and server hash the seed to determine which specific
IPv6 address from the set of prefixes will be used and registered as a dark
decoy. It may seem intuitive to instead have the client
send the specific IP address to register, but allowing the client arbitrary
choice also allows the censor to register suspected dark decoys and block them if
they pick up. 
By using a hash of a seed, the censor would have to pre-image the hash to
obtain a seed it could use to register for a desired IP address.
It also gives a
secret (the seed) that only the client and station know, even after the client
connects to the dark decoy address.

Once the dark decoy IP address has been selected, the station watches for
packets destined to that address, and forwards them onto the dark decoy
\textbf{application}. The station can also optionally ignore packets not from
the source IP address of the registering client, so that to a probing censor
from a different IP address,
the dark decoy appears to be firewalled off from all but the client. We note
this is not a robust solution: censors have previously been observed taking over
IP addresses of clients~\cite{ensafi-tor}. We instead address active probing in
the application.

\subsubsection{IPv6 vs IPv4 dark decoys}

Dark decoy IP addresses must be derived from network blocks that are routed (so they pass
the ISP station) and contain other legitimate hosts (so that censors cannot
block the entire network without collateral damage).
Because of the large number of IPv6 addresses, even
relatively small network prefixes have astronomical numbers of addresses: a
single /32 prefix has $2^{96}$ possible addresses. Therefore, client-chosen
seeds have negligible probability of corresponding to addresses that are already
being used by legitimate hosts. This allows us to select dark decoy addresses
from network prefixes that contain
legitimate hosts---crucial to discouraging the censor from blocking them
outright---without worry that registrations could interfere with legitimate
services.

In addition, the use of IPv6 prevents censors from exhaustively probing
potential dark decoy network prefixes ahead of time to learn the full set of
legitimate sites in the network.

\paragraph{IPv4}
While \scheme composes well with IPv6, we can also support IPv4,
at the cost of being vulnerable to active probing by the censor.
We emphasize that TapDance is already
vulnerable to active probing attacks~\cite{tapdance14} that \scheme defends
against when using IPv6. However, in IPv4, there are substantially fewer
addresses, allowing censors to easily enumerate network prefixes that pass by
the ISP station and measure legitimate sites. Furthermore, the small address
space makes it much easier to pre-image the hash used to derive IP addresses
from the seed. Registering a specific IPv4 address in an IPv4 /16 subnet will
take only an expected $2^{16}$ hashes for the censor to achieve. This would let
attackers register legitimate hosts as dark decoys, potentially disrupting
legitimate service. If the station refused to pick up for addresses that
correspond to legitimate hosts (measured by scanning during registration), then
censors could use this as an oracle for distinguishing legitimate sites from
dark decoys. Still, IPv4 \scheme offers many performance, flexibility, and
simplicity benefits over TapDance, though they are both vulnerable to active
probing attacks.

%While address utilization in IPv4 is quite high (all blocks have been allocated
%at the RIR level), the fraction of addresses that respond to TCP connections on
%a given port is quite low: even popular ports like 443 (use by TLS) have less
%than 2\% of IPv4 hosts respond to connection requests. This leaves a large
%number of hosts available to use as dark decoys. However, if a client registers
%a dark decoy address that is already happens to be used by an existing host,
%there will be multiple responses when the client tries to connect, and the
%connection will fail. However, this failure is still limited to the registering
%client, as the application only responds to the IP of the client that
%registered. In IPv6, the odds of picking a legitimate host are negligible: with
%a /32 prefix of IPv6, there are $2^{96}$ addresses to choose from.
%\nikita{/32 is pretty big, e.g. UIUC only has a /48}
